### 2020-01-18 nlp_models.tex
moved methods nlp to nlp

Explain why Log Norm is sooo large...alpha is off may need to prune the alpha

>>>>

We find that in the pretrained GPT models, the first embedding layer(s) have unusually large eigenvalues,
reflecting a lack of normalization.  For example, in GPT, most layers, the maximum eigenvalue $\lambda_{max}\sim\mathcal{O}(10-100)$, 
but in the first embedding layer, the maximum is of order N (the number of words in the embedding), or
 $\lambda_{max}\sim\mathcal{O}(10^{5})$.  For GPT and GPT2, we layer all layers as-is (although one may to normalize
the first 2 layers by  $\mathbf{X}$ by $\frac{1}{N}$, or to treat them as an outlier); including them does
not significantly alter the results here.
